---
title: "R Notebook"
output: html_notebook
---
Optional, after L1 clustering remove clusters that seem to be doublets or otherwise bad quality cells
```{r}
networkExpressionFile <- networkExpressionFile[,names(subset(SCN3Elevel1,! SCN3Elevel1 %in% c("1")))]
networkAnnotableFile <- networkAnnotableFile[colnames(networkExpressionFile),]
```
Filter out NaN and Na
```{r}
#mt-
#Mt-
#MT-
#see if you grep something
table(grepl("ERCC.",rownames(networkExpressionFile)))
networkExpressionFile <- networkExpressionFile[! grepl("ERCC.",rownames(networkExpressionFile)),]
#see if you grep something
table(grepl("Mt.",rownames(networkExpressionFile)))
networkExpressionFile <- networkExpressionFile[! grepl("Mt.",rownames(networkExpressionFile)),]
 filtercells <- apply(networkExpressionFile,2,function(x) anyNA(x))
networkExpressionFile <- as.matrix(networkExpressionFile[,!filtercells])
filtercells <- apply(networkExpressionFile,2,function(x) any(x=="NaN"))
networkExpressionFile <- as.matrix(networkExpressionFile[,!filtercells])
networkAnnotableFile <- networkAnnotableFile[colnames(networkExpressionFile),]
networkExpressionFile <-networkExpressionFile-min(networkExpressionFile)
rm(filtercells)
```
Remove genes that are only expressed in a few cells
```{r}
expr_limit <- mean(networkExpressionFile)
expressed_genes <- 1*apply(networkExpressionFile,1,function(x) (x) > expr_limit)
expressed_genes <- apply(expressed_genes,2,function(x) sum(x) >= 1)
networkExpressionFile <- networkExpressionFile[expressed_genes,]
rm(expressed_genes)
```
Feature selection
```{r}
CVsq <- function(x) {(sd(x)/mean(x))^2}
expr_limit <- mean(networkExpressionFile)
emat_expressed <- apply(networkExpressionFile,1,function(x) any ((x) > expr_limit))
emat_expressed <- networkExpressionFile[emat_expressed,]
CV2 <- apply(emat_expressed,1,CVsq)
meancounts <- apply(emat_expressed,1,mean)
CV2_matrix <- matrix(c(log(meancounts),log(CV2)),nrow = length(CV2),ncol = 2)
row.names(CV2_matrix) <- names(CV2)
colnames(CV2_matrix) <- c("LogExpr","CV2")
CV2_matrix <- as.data.frame(CV2_matrix)
library(e1071)
model <- svm(CV2 ~ LogExpr ,CV2_matrix, gamma = 0.06)
predictedY <- predict(model, CV2_matrix)
CV2_matrix <- cbind(CV2_matrix,predictedY)
CV2_matrix$RelativeVariance <-CV2_matrix$CV2 - CV2_matrix$predictedY
NormGenes <- row.names(subset(CV2_matrix, RelativeVariance >= 0.0))
NormGenesFactor <- as.factor(1*(CV2_matrix$RelativeVariance >= 0.0))
palette("default")
plot(CV2_matrix$LogExpr,CV2_matrix$CV2,xlab ="Mean Count Magnitude (log)",ylab="Squared Coefficient of Variation", pch=20, cex=0.3, col=NormGenesFactor)
points(CV2_matrix$LogExpr,predictedY, col="green",pch=20, cex=0.1)
length(NormGenes)
NormGenes <- subset(NormGenes,! NormGenes %in% c("Xist","Tsix"))
featureselection <- NormGenes
SCN3Egeneset <- featureselection
#SCN3Egeneset <- intersect(featureselection,L1L2markers)
#SCN3Egeneset <- L1L2markers
rm(CV2,CV2_matrix,emat_expressed,meancounts,model,NormGenes,NormGenesFactor,predictedY,SCN3Egeneset)
```
```{r}
savenetworkdf <- networkExpressionFile
#networkExpressionFile <- savenetworkdf
```
#Spatially filter genes with auto bootstrapping
```{r}
gc()
threshold <- 1 #use mean spatial correlation of geneset of the featureselection (1) or after the first round of filtering (2) (more strict, which is default) 
SCN3Egeneset <- featureselection
originalnetworkdf <- networkExpressionFile
if(ncol(networkExpressionFile)>15000){
bootstrap<-1
sample<-1
moransIsampled <- as.character(NULL)
}
if(ncol(networkExpressionFile)<=15000)
{
  bootstrap<-4
  sample<-0
  }
while(bootstrap<5){
SCN3Egeneset <- featureselection
iter=0
meanMoran<-0
if(sample==1){
networkExpressionFile  <- originalnetworkdf[,sample(ncol(originalnetworkdf), 5000) ]
print(paste("bootstrapping...","round",bootstrap))
}
OldGeneset <- as.character(seq_len(100000))
while(length(OldGeneset) != length(SCN3Egeneset) ){
 iter=iter+1
  library(amap)
#library(MASS)
#library(destiny)
library(dpt)
#library(Matrix)
#library(diffusionMap)
print(paste("Preparing genefiltering on", length(SCN3Egeneset), "genes."))
print("Making celllandscape...Filtering possible duplicated cells in original file")
#if(length(OldGeneset)==100000)
#{
#  pca <- prcomp(t(log(networkExpressionFile[featureselection,]+1)),scale. = FALSE)
#  cd_diffusionplot <-pca$x[,c(1:30)]
#  }

#if(length(OldGeneset)!=100000){cd_diffusionplot <- t(log(networkExpressionFile[SCN3Egeneset,]+1))}
pca <- prcomp(t(log(networkExpressionFile[SCN3Egeneset,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
#cd_diffusionplot <- t(log(networkExpressionFile[SCN3Egeneset,]+1))
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
print("Making celllandscape...Making diffusionmap")
ts <- Transitions(cd_diffusionplot,k=20)


#Gene filtering
print(paste("Filtering", length(SCN3Egeneset), "genes."))
OldGeneset <- SCN3Egeneset
NetworkDist <- as.matrix(ts@transitions)
#NetworkDist <- distcells*distcells2
colnames(NetworkDist) <- row.names(cd_diffusionplot)
row.names(NetworkDist) <- row.names(cd_diffusionplot)
emat_expressed <- apply(networkExpressionFile,1,function(x) any ((x) >expr_limit))
emat_expressed <- networkExpressionFile[emat_expressed,row.names(NetworkDist)]
emat_expressed <- as.matrix(emat_expressed[intersect(row.names(emat_expressed),OldGeneset),])

library(doParallel)
library(foreach)

library(spdep)
cores <- detectCores()
cl <- makeCluster(cores)  
registerDoParallel(cl)  
SCN3Egenefilter <- matrix(nrow=nrow(emat_expressed),ncol = 3) 
cellnames <- colnames(emat_expressed)
spatial.weights <- mat2listw(NetworkDist)
numbsim <- 1
test <- foreach(i=1:nrow(emat_expressed),.packages="spdep",.combine=cbind) %dopar% 
{
 x <- emat_expressed[i,]
 r <- row.names(emat_expressed)[i]
 m <- c(unlist(moran.mc(x,spatial.weights,nsim=numbsim,zero.policy = TRUE))[1:3],r)
}

stopCluster(cl)
SCN3Egenefilter <- t(test)
SCN3Egenefilter <- SCN3Egenefilter[! apply(SCN3Egenefilter,1,function(x) any(x=="NaN")),]
row.names(SCN3Egenefilter) <- SCN3Egenefilter[,4]
SCN3Egenefilter_clean <- as.data.frame(SCN3Egenefilter[complete.cases(SCN3Egenefilter),c(1:3)])
r <- row.names(SCN3Egenefilter_clean)
SCN3Egenefilter_clean <- apply(SCN3Egenefilter_clean,2,function(x) as.numeric(x))
row.names(SCN3Egenefilter_clean) <- r


#if(meanMoran==0){meanMoran<-mean(SCN3Egenefilter_clean[,1])}
if(iter<=threshold){meanMoran<-mean(SCN3Egenefilter_clean[,1],na.rm=TRUE)}
SCN3Egeneset <- row.names(SCN3Egenefilter_clean[SCN3Egenefilter_clean[,1] >= meanMoran,])

}
bootstrap <- bootstrap+1
if(sample==1){
moransIsampled <- c(moransIsampled,SCN3Egeneset)
}
}
networkExpressionFile <- originalnetworkdf
GeneMarkov1 <- SCN3Egeneset
if(sample==1){GeneMarkov <- unique(moransIsampled)}
#L1geneset <- GeneMarkov
rm(emat_expressed,NetworkDist,SCN3Egenefilter,test,cellnames,cl,cores,i,iter,meanMoran,numbsim,OldGeneset,r,SCN3Egeneset,spatial.weights)
if(sample==1)
{
  print("Making final celllandscape...Filtering possible duplicated cells in original file")
  #cd_diffusionplot <- t(log(networkExpressionFile[GeneMarkov,]+1))
  pca <- prcomp(t(log(networkExpressionFile[GeneMarkov,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
print("Making final celllandscape...Making diffusionmap. This can take a while...")
ts <- Transitions(cd_diffusionplot,k=20)
  }
print("Done with part one... Starting part two...")

gc()

SCN3Egeneset <- featureselection
originalnetworkdf <- networkExpressionFile
if(ncol(networkExpressionFile)>15000){
bootstrap<-1
sample<-1
moransIsampled <- as.character(NULL)
}
if(ncol(networkExpressionFile)<=15000)
{
  bootstrap<-4
  sample<-0
  }
while(bootstrap<5){
SCN3Egeneset <- featureselection
iter=0
meanMoran<-0
if(sample==1){
networkExpressionFile  <- originalnetworkdf[,sample(ncol(originalnetworkdf), 5000) ]
print(paste("bootstrapping...","round",bootstrap))
}
OldGeneset <- as.character(seq_len(100000))
while(length(GeneMarkov1) < (length(SCN3Egeneset)) ){
 iter=iter+1
  library(amap)
#library(MASS)
#library(destiny)
library(dpt)
#library(Matrix)
#library(diffusionMap)
print(paste("Preparing genefiltering on", length(SCN3Egeneset), "genes."))
print("Making celllandscape...Filtering possible duplicated cells in original file")
#if(length(OldGeneset)==100000)
#{
#  pca <- prcomp(t(log(networkExpressionFile[featureselection,]+1)),scale. = FALSE)
#  cd_diffusionplot <-pca$x[,c(1:30)]
#  }

#if(length(OldGeneset)!=100000){cd_diffusionplot <- t(log(networkExpressionFile[SCN3Egeneset,]+1))}
pca <- prcomp(t(log(networkExpressionFile[SCN3Egeneset,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
#cd_diffusionplot <- t(log(networkExpressionFile[SCN3Egeneset,]+1))
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
print("Making celllandscape...Making diffusionmap")
ts <- Transitions(cd_diffusionplot,k=20)


#Gene filtering
print(paste("Filtering", length(SCN3Egeneset), "genes."))
OldGeneset <- SCN3Egeneset
NetworkDist <- as.matrix(ts@transitions)
#NetworkDist <- distcells*distcells2
colnames(NetworkDist) <- row.names(cd_diffusionplot)
row.names(NetworkDist) <- row.names(cd_diffusionplot)
emat_expressed <- apply(networkExpressionFile,1,function(x) any ((x) >expr_limit))
emat_expressed <- networkExpressionFile[emat_expressed,row.names(NetworkDist)]
emat_expressed <- as.matrix(emat_expressed[intersect(row.names(emat_expressed),OldGeneset),])

library(doParallel)
library(foreach)

library(spdep)
cores <- detectCores()
cl <- makeCluster(cores)  
registerDoParallel(cl)  
SCN3Egenefilter <- matrix(nrow=nrow(emat_expressed),ncol = 3) 
cellnames <- colnames(emat_expressed)
spatial.weights <- mat2listw(NetworkDist)
numbsim <- 1
networkdist <- 1-NetworkDist
test <- foreach(i=1:nrow(emat_expressed),.packages="spdep",.combine=cbind) %dopar% 
{
 x <- emat_expressed[i,]
 x <- x[x>expr_limit]
 if(length(x)<2){}
 else{
 r <- row.names(emat_expressed)[i]
 y <- networkdist[names(x),names(x)]
 a <- mean(y)
 y <- nrow(y)
 m <- c(a,y,r)
 }
}

stopCluster(cl)
SCN3Egenefilter <- t(test)
SCN3Egenefilter <- SCN3Egenefilter[! apply(SCN3Egenefilter,1,function(x) any(x=="NaN")),]
row.names(SCN3Egenefilter) <- SCN3Egenefilter[,3]
SCN3Egenefilter_clean <- as.data.frame(SCN3Egenefilter[complete.cases(SCN3Egenefilter),c(1:2)])
r <- row.names(SCN3Egenefilter_clean)
SCN3Egenefilter_clean <- apply(SCN3Egenefilter_clean,2,function(x) as.numeric(x))
row.names(SCN3Egenefilter_clean) <- r

SCN3Egenefilter_clean2 <- SCN3Egenefilter_clean
SCN3Egenefilter_clean2[,1] <- log(SCN3Egenefilter_clean2[,1]+1)
library(e1071)
model <- svm(V1 ~ V2 ,SCN3Egenefilter_clean2,gamma = 10)
predictedY <- predict(model, SCN3Egenefilter_clean2)
SCN3Egenefilter_clean2 <- SCN3Egenefilter_clean2[names(predictedY),]
CV2_matrix <- as.data.frame(cbind(SCN3Egenefilter_clean2,predictedY))
CV2_matrix$RelativeVariance <-CV2_matrix[,1] - CV2_matrix[,3]
SCN3Egeneset <- row.names(subset(CV2_matrix, RelativeVariance < 0))
}
bootstrap <- bootstrap+1
if(sample==1){
moransIsampled <- c(moransIsampled,SCN3Egeneset)
}
}
networkExpressionFile <- originalnetworkdf
GeneMarkov <- unique(c(SCN3Egeneset,GeneMarkov1))
if(sample==1){GeneMarkov <- unique(moransIsampled)}
L1geneset <- GeneMarkov
rm(emat_expressed,NetworkDist,SCN3Egenefilter,test,cellnames,cl,cores,i,iter,meanMoran,numbsim,OldGeneset,r,SCN3Egeneset,spatial.weights)

  print("Making final celllandscape...Filtering possible duplicated cells in original file")
  #cd_diffusionplot <- t(log(networkExpressionFile[GeneMarkov,]+1))
  pca <- prcomp(t(log(networkExpressionFile[GeneMarkov,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
#library(Matrix)
#cd_diffusionplot <- Matrix(cd_diffusionplot, sparse = TRUE)
print("Making final celllandscape...Making diffusionmap. This can take a while...")
ts <- Transitions(cd_diffusionplot,k=20)
  
print("Done.")

```
Estimate the number of Level1 classes, using cluster estimation and tSNE, try diffent numbers of PCA components
```{r}
gc()
SCN3Egeneset <- GeneMarkov
library(factoextra)
pca <- prcomp(as.matrix(ts@transitions),scale. = FALSE)
plot(pca$sdev[1:50],pch = 20,
xlab = 'Diffusion component (DC)', ylab = 'sdev')
Networkdist <- as.dist(1-as.matrix(ts@transitions))
fviz_nbclust(pca$x[,c(1:3)],diss=, hcut, method = "silhouette",
             hc_method = "ward.D2",k.max = 20)

```
```{r}
#View(as.matrix(ts@transitions))
#Networkdist <- 1*(as.matrix(ts@transitions) > 0)
Networkdist <- as.matrix(ts@transitions)
colnames(Networkdist) <- row.names(cd_diffusionplot)
row.names(Networkdist) <- row.names(cd_diffusionplot)
library(igraph)
L1graph <- graph_from_adjacency_matrix(Networkdist,weighted = TRUE,mode="undirected")
L1graphSupercells <- cluster_walktrap(L1graph,weights=E(L1graph)$weight,step=50,merges=TRUE)
table(L1graphSupercells$membership)

#L1graphSupercells <- cluster_fast_greedy(L1graph,weights=E(L1graph)$weight)
#table(L1graphSupercells$membership)
SCN3Elevel1 <- as.factor(L1graphSupercells$membership)
names(SCN3Elevel1) <- L1graphSupercells$names
Networkdist <- as.dist(1-Networkdist)
```
Generate tSNE coordinates
```{r, message=FALSE, warning=FALSE, include=FALSE}
pcatsne <- prcomp(t(log(networkExpressionFile[GeneMarkov,]+1)),scale. = FALSE)
tsne <- t(pcatsne$x[,c(1:30)])
#tsne <- Networkdist
#tsne <- z$H[-c(29,31:33),]
library(Rtsne)
set.seed(123456789)
tsne_out <- Rtsne(t(tsne), initial_dims=100, perplexity=round(7+(0.01*ncol(networkExpressionFile)),0),max_iter = 1000,check_duplicates = FALSE,
                  verbose = TRUE, theta = 0.5, pca = FALSE)
#rownames(tsne_out$Y) <- colnames(tsne)
```
Do Level1 clustering and split the dataset for downstream clustering
```{r, fig.height=5}
library(heatmap3)
library(viridis)
clusterdata <- as.data.frame(t((1*(apply(networkExpressionFile[GeneMarkov,row.names(cd_diffusionplot)],1,function(x) (x) >expr_limit)))))
clusterdata <- clusterdata[apply(clusterdata,1,function(x) var(x) > 0),apply(clusterdata,2,function(x) var(x) > 0)]
library(cluster)
distpca <- pca$x[,c(1:3)]
row.names(distpca) <- row.names(cd_diffusionplot)
distpca <- distpca[colnames(clusterdata),]
SCN3E_hc <- hclust(dist(distpca,method="manhattan"), method = "ward.D2")
#SCN3E_hc <- hclust(Networkdist, method = "ward.D2")
SCN3Ecluster <- rbind(groups = cutree(SCN3E_hc, k=4))
names(SCN3Ecluster) <- row.names(distpca)

pcagene <- prcomp(log(networkExpressionFile[row.names(clusterdata),]+1),scale. = FALSE)
pcageneexpression <- pcagene$x[,c(1:50)]
SCN3E_hc_gene <- hclust(dist(pcageneexpression,method="manhattan"), method = "ward.D2")


library("dendsort")

SCN3E_hc <- dendsort(SCN3E_hc, type="min")
SCN3E_hc_gene <- dendsort(SCN3E_hc_gene, type="min")
palette <- rainbow(length(levels(as.factor(SCN3Ecluster))))
cols <- palette[as.factor(SCN3Ecluster)]
#cols <- palette[as.factor(FinalClustersOrdered)]
#pdf("~/Documents/SingleCellData/IdoDAM/L1clusteringheatmapNew.pdf",width = 20,height = 30,useDingbats=FALSE)
heatmap3(clusterdata,ColSideColors=cols, Rowv = as.dendrogram(SCN3E_hc_gene) , Colv = as.dendrogram(SCN3E_hc) ,scale = "col",symm = F, method = "ward.D2",col=viridis(256),balanceColor =F,cexRow = 0.8)
legend("topright", legend=levels(as.factor(SCN3Ecluster)),
   col=palette,
   pch=19)
#pdf("~/Documents/SingleCellData/IdoDAM/L1clusteringtSNE.pdf",width = 10,height = 10,useDingbats=FALSE)
plot(tsne_out$Y,col=cols,pch=20,cex=1)
legend("topright", legend=levels(as.factor(SCN3Ecluster)),
   col=palette,
   pch=19)

SCN3Elevel1 <- as.factor(SCN3Ecluster)
table(SCN3Elevel1)
```


Visualize expression
```{r, fig.width=5}
library(ggplot2)
Expression <- as.data.frame(t(log(networkExpressionFile+1)))
#Expression <- as.data.frame(t(z$H))
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Expression$Lpl)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")
```

First we generate markers for each of the clusters
```{r}
library(MAST)
library(NMF)
networkExpressionFilesub <- networkExpressionFile[,colnames(clusterdata)]
networkAnnotableFilesub <- networkAnnotableFile[colnames(clusterdata),]

diffclusters <- droplevels(as.factor(SCN3Elevel1))
names(diffclusters) <- rownames(networkAnnotableFilesub)
table(diffclusters)
NetworkMASTobj <- FromMatrix(networkExpressionFilesub[featureselection,], as.data.frame(as.character(diffclusters)))
thres <- thresholdSCRNACountMatrix(assay(NetworkMASTobj), nbins = 10, min_per_bin = 50,bin_by = "median",data_log = FALSE)#,adj = 1)
assays(NetworkMASTobj) <- list(thresh=thres$counts_threshold, tpm=assay(NetworkMASTobj))
cdr2 <-colSums(assay(NetworkMASTobj)>mean(networkExpressionFile))
colData(NetworkMASTobj)$cngeneson <- scale(cdr2)
options(mc.cores=1)
zlmCond <- zlm(~diffclusters + cngeneson, NetworkMASTobj)
show(zlmCond)
zlm.lr <- lrTest(zlmCond, 'diffclusters')
FDR <- p.adjust(zlm.lr[,,'Pr(>Chisq)'][,3],"fdr")
diffgenes <- names(FDR[FDR < 0.01])
sigtest <- diffgenes
summaryDt <- summary(zlmCond)
test <- print(summaryDt,n=nrow(NetworkMASTobj))
row.names(test) <- test[,1]
rown <- row.names(test)
test <- test[,-c(1)]
diffclusters1 <- 0
test <- cbind(diffclusters1,test)
test <- t(apply(test,1,function (x)gsub("*", "", x, fixed = TRUE)))
test <- apply(test,2,as.numeric)
row.names(test) <- rown
DifferentialGenestest <- t(apply(test,1,function(x) x-mean(x,na.rm=TRUE)))
DifferentialGenestest <- DifferentialGenestest[sigtest,-2]
markersMAST <- scale(DifferentialGenestest)
marker <- t(scale(t(markersMAST)))
MarkerGeneList <- subset(row.names(marker),! row.names(marker) %in% c("Xist","Tsix","marker-GFP"))



L1names <- levels(SCN3Elevel1)
####Optional 
#Name the clusters
#L1names <-paste(c("OL","NPROG","EVLMC","VLMC","NBLAST"),L1names,sep=".cluster")
#####
L1Markerslist <- MarkerGeneList
```
Save the files
```{r}
write.table(DifferentialGenestest,file = paste("~/Documents/SingleCellData/IdoDAM/ClustersZ_Lvl1.txt",sep=""), sep="\t",row.names = TRUE, col.names = TRUE, quote = FALSE)
write.table(test,file = paste("~/Documents/SingleCellData/IdoDAM/ClustersLvl1.txt",sep=""), sep="\t",row.names = TRUE, col.names = TRUE, quote = FALSE)
```
L2 clustering, Now we split the data and repeat the clustering 

Only do this once because it wipes the previous clusterinformation
```{r, fig.height=5}
#Reset genelist
expr_limit <- 0
NetworkClusters <- as.character(NULL)
L2markerlist <- as.character(NULL)
L2markovlist <- as.character(NULL)
namesNetworkClusters <- as.character(NULL)
##########Indicate the clusternumber by setting i
```
Set i to the sub-cluster
```{r}
 i=4
```
```{r}
threshold <- 2 #use mean spatial correlation of geneset of the featureselection (1) or after the first round of filtering (2) (more strict, which is default) 
networksubset <- networkExpressionFile[,names(subset(SCN3Elevel1, SCN3Elevel1 %in% i))]
dim(networksubset)
clusternumber <- i
print(paste("Working on cluster",clusternumber, nrow(networksubset),"Genes",ncol(networksubset),"Cells"))
CVsq <- function(x) {(sd(x)/mean(x))^2}
expr_limit <- mean(networkExpressionFile)
emat_expressed <- apply(networksubset,1,function(x) any ((x) > expr_limit))
emat_expressed <- networksubset[emat_expressed,]
CV2 <- apply(emat_expressed,1,CVsq)
meancounts <- apply(emat_expressed,1,mean)
CV2_matrix <- matrix(c(log(meancounts),log(CV2)),nrow = length(CV2),ncol = 2)
row.names(CV2_matrix) <- names(CV2)
colnames(CV2_matrix) <- c("LogExpr","CV2")
CV2_matrix <- as.data.frame(CV2_matrix)
library(e1071)
model <- svm(CV2 ~ LogExpr ,CV2_matrix)#, gamma = 0.06)
predictedY <- predict(model, CV2_matrix)
CV2_matrix <- cbind(CV2_matrix,predictedY)
CV2_matrix$RelativeVariance <-CV2_matrix$CV2 - CV2_matrix$predictedY
NormGenes <- row.names(subset(CV2_matrix, RelativeVariance >= 0.0))
NormGenesFactor <- as.factor(1*(CV2_matrix$RelativeVariance >= 0.0))
palette("default")
plot(CV2_matrix$LogExpr,CV2_matrix$CV2,xlab ="Mean Count Magnitude (log)",ylab="Squared Coefficient of Variation", pch=20, cex=0.3, col=NormGenesFactor)
points(CV2_matrix$LogExpr,predictedY, col="green",pch=20, cex=0.1)
length(NormGenes)
NormGenes <- subset(NormGenes,! NormGenes %in% c("Xist","Tsix","eGFP"))
featureselection <- NormGenes
featureselection <- NormGenes
SCN3Egeneset <- featureselection
SCN3Egeneset2 <- featureselection

iter=0
meanMoran<-0
OldGeneset <- as.character(seq_len(100000))
while(length(OldGeneset) != length(SCN3Egeneset) ){
  iter=iter+1
library(dpt)
pca <- prcomp(t(log(networksubset[SCN3Egeneset,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
#cd_diffusionplot <- t(log(networksubset[SCN3Egeneset,]+1))
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
ts <- Transitions(cd_diffusionplot,k=20)
#Gene filtering
print(paste("Filtering", length(SCN3Egeneset), "genes."))
OldGeneset <- SCN3Egeneset
NetworkDist <- as.matrix(ts@transitions)
colnames(NetworkDist) <- row.names(cd_diffusionplot)
row.names(NetworkDist) <- row.names(cd_diffusionplot)
emat_expressed <- apply(networksubset,1,function(x) any ((x) >expr_limit))
emat_expressed <- networksubset[emat_expressed,row.names(NetworkDist)]
emat_expressed <- as.matrix(emat_expressed[intersect(row.names(emat_expressed),OldGeneset),])
library(doParallel)
library(foreach)

library(spdep)
cores <- detectCores()
cl <- makeCluster(cores)  
registerDoParallel(cl)  
i<-1
SCN3Egenefilter <- matrix(nrow=nrow(emat_expressed),ncol = 3) 
cellnames <- colnames(emat_expressed)
spatial.weights <- mat2listw(NetworkDist)
numbsim <- 1
networkdist <- 1-NetworkDist
library(ape)
library(spdep)
test <- foreach(i=1:nrow(emat_expressed),.packages="spdep",.combine=cbind) %dopar% 
{
 x <- emat_expressed[i,]
 r <- row.names(emat_expressed)[i]
 m <- c(unlist(moran.mc(x,spatial.weights,nsim=numbsim,zero.policy = TRUE))[1:3],r)
 
}

stopCluster(cl)
SCN3Egenefilter <- t(test)
SCN3Egenefilter <- SCN3Egenefilter[! apply(SCN3Egenefilter,1,function(x) any(x=="NaN")),]
row.names(SCN3Egenefilter) <- SCN3Egenefilter[,4]
SCN3Egenefilter_clean <- as.data.frame(SCN3Egenefilter[complete.cases(SCN3Egenefilter),c(1:3)])
r <- row.names(SCN3Egenefilter_clean)
SCN3Egenefilter_clean <- apply(SCN3Egenefilter_clean,2,function(x) as.numeric(x))
row.names(SCN3Egenefilter_clean) <- r


#if(meanMoran==0){meanMoran<-mean(SCN3Egenefilter_clean[,1])}
if(iter<=threshold){meanMoran<-mean(SCN3Egenefilter_clean[,1],na.rm=TRUE)}
SCN3Egeneset2 <- row.names(SCN3Egenefilter_clean[SCN3Egenefilter_clean[,1] >= meanMoran,])

SCN3Egeneset <- SCN3Egeneset2
}

expr_limit <- mean(networksubset)
expressed_genes <- 1*apply(networksubset[SCN3Egeneset,],1,function(x) (x) > expr_limit)
expressed_genes <- apply(expressed_genes,2,function(x) sum(x) < ncol(networksubset))
SCN3Egeneset <- intersect(row.names(networkExpressionFile[expressed_genes,]),SCN3Egeneset)
rm(expressed_genes)

GeneMarkov1 <- SCN3Egeneset
rm(cd_diffusionplot,emat_expressed,NetworkDist,SCN3Egenefilter,test,cellnames,cl,cores,i,iter,meanMoran,numbsim,OldGeneset,r,SCN3Egeneset,spatial.weights)

i<- clusternumber
threshold <- 2 #use mean spatial correlation of geneset of the featureselection (1) or after the first round of filtering (2) (more strict, which is default) 
networksubset <- networkExpressionFile[,names(subset(SCN3Elevel1, SCN3Elevel1 %in% i))]
dim(networksubset)
clusternumber <- i
print(paste("Working on cluster",clusternumber, nrow(networksubset),"Genes",ncol(networksubset),"Cells"))
CVsq <- function(x) {(sd(x)/mean(x))^2}
expr_limit <- mean(networkExpressionFile)
emat_expressed <- apply(networksubset,1,function(x) any ((x) > expr_limit))
emat_expressed <- networksubset[emat_expressed,]
CV2 <- apply(emat_expressed,1,CVsq)
meancounts <- apply(emat_expressed,1,mean)
CV2_matrix <- matrix(c(log(meancounts),log(CV2)),nrow = length(CV2),ncol = 2)
row.names(CV2_matrix) <- names(CV2)
colnames(CV2_matrix) <- c("LogExpr","CV2")
CV2_matrix <- as.data.frame(CV2_matrix)
library(e1071)
model <- svm(CV2 ~ LogExpr ,CV2_matrix)#, gamma = 0.06)
predictedY <- predict(model, CV2_matrix)
CV2_matrix <- cbind(CV2_matrix,predictedY)
CV2_matrix$RelativeVariance <-CV2_matrix$CV2 - CV2_matrix$predictedY
NormGenes <- row.names(subset(CV2_matrix, RelativeVariance >= 0.0))
NormGenesFactor <- as.factor(1*(CV2_matrix$RelativeVariance >= 0.0))
palette("default")
plot(CV2_matrix$LogExpr,CV2_matrix$CV2,xlab ="Mean Count Magnitude (log)",ylab="Squared Coefficient of Variation", pch=20, cex=0.3, col=NormGenesFactor)
points(CV2_matrix$LogExpr,predictedY, col="green",pch=20, cex=0.1)
length(NormGenes)
NormGenes <- subset(NormGenes,! NormGenes %in% c("Xist","Tsix","eGFP"))
featureselection <- NormGenes
featureselection <- NormGenes
SCN3Egeneset <- featureselection
SCN3Egeneset2 <- featureselection

iter=0
meanMoran<-0
OldGeneset <- as.character(seq_len(100000))
while(length(GeneMarkov1) < (length(SCN3Egeneset)) ){
  iter=iter+1
library(dpt)
pca <- prcomp(t(log(networksubset[SCN3Egeneset,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
#cd_diffusionplot <- t(log(networksubset[SCN3Egeneset,]+1))
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
ts <- Transitions(cd_diffusionplot,k=20)
#Gene filtering
print(paste("Filtering", length(SCN3Egeneset), "genes."))
OldGeneset <- SCN3Egeneset
NetworkDist <- as.matrix(ts@transitions)
colnames(NetworkDist) <- row.names(cd_diffusionplot)
row.names(NetworkDist) <- row.names(cd_diffusionplot)
emat_expressed <- apply(networksubset,1,function(x) any ((x) >expr_limit))
emat_expressed <- networksubset[emat_expressed,row.names(NetworkDist)]
emat_expressed <- as.matrix(emat_expressed[intersect(row.names(emat_expressed),OldGeneset),])
library(doParallel)
library(foreach)

library(spdep)
cores <- detectCores()
cl <- makeCluster(cores)  
registerDoParallel(cl)  
i<-1
SCN3Egenefilter <- matrix(nrow=nrow(emat_expressed),ncol = 3) 
cellnames <- colnames(emat_expressed)
spatial.weights <- mat2listw(NetworkDist)
numbsim <- 1
networkdist <- 1-NetworkDist
library(ape)
library(spdep)
test <- foreach(i=1:nrow(emat_expressed),.packages="spdep",.combine=cbind) %dopar% 
{
 x <- emat_expressed[i,]
 x <- x[x>expr_limit]
 if(length(x)<2){}
 else{
 r <- row.names(emat_expressed)[i]
 y <- networkdist[names(x),names(x)]
 a <- mean(y)
 y <- nrow(y)
 m <- c(a,y,r)
 }
}

stopCluster(cl)
SCN3Egenefilter <- t(test)
SCN3Egenefilter <- SCN3Egenefilter[! apply(SCN3Egenefilter,1,function(x) any(x=="NaN")),]
row.names(SCN3Egenefilter) <- SCN3Egenefilter[,3]
SCN3Egenefilter_clean <- as.data.frame(SCN3Egenefilter[complete.cases(SCN3Egenefilter),c(1:2)])
r <- row.names(SCN3Egenefilter_clean)
SCN3Egenefilter_clean <- apply(SCN3Egenefilter_clean,2,function(x) as.numeric(x))
row.names(SCN3Egenefilter_clean) <- r

SCN3Egenefilter_clean2 <- SCN3Egenefilter_clean
SCN3Egenefilter_clean2[,1] <- log(SCN3Egenefilter_clean2[,1]+1)
library(e1071)
model <- svm(V1 ~ V2 ,SCN3Egenefilter_clean2,gamma = 10)
predictedY <- predict(model, SCN3Egenefilter_clean2)
SCN3Egenefilter_clean2 <- SCN3Egenefilter_clean2[names(predictedY),]
CV2_matrix <- as.data.frame(cbind(SCN3Egenefilter_clean2,predictedY))
CV2_matrix$RelativeVariance <-CV2_matrix[,1] - CV2_matrix[,3]
SCN3E_genes2 <- row.names(subset(CV2_matrix, RelativeVariance < 0))
#NormGenesFactor <- as.factor(1*(CV2_matrix$RelativeVariance < 0))
#palette("default")
#plot(CV2_matrix$V5,CV2_matrix$V4,xlab ="Mean Cell Count Magnitude (log)",ylab="Mean Distance in Network (log)", pch=20, cex=0.1, col=NormGenesFactor)
#points(CV2_matrix$V5,CV2_matrix$predictedY, col="green",pch=20, cex=0.3)
#length(SCN3E_genes2)

SCN3Egeneset <- SCN3E_genes2
#SCN3Egeneset <- SCN3Egeneset2
}

expr_limit <- mean(networksubset)
expressed_genes <- 1*apply(networksubset[SCN3Egeneset,],1,function(x) (x) > expr_limit)
expressed_genes <- apply(expressed_genes,2,function(x) sum(x) < ncol(networksubset))
SCN3Egeneset <- intersect(row.names(networkExpressionFile[expressed_genes,]),SCN3Egeneset)
rm(expressed_genes)

GeneMarkov <- unique(c(GeneMarkov1,SCN3Egeneset))
rm(cd_diffusionplot,emat_expressed,NetworkDist,SCN3Egenefilter,test,cellnames,cl,cores,i,iter,meanMoran,numbsim,OldGeneset,r,SCN3Egeneset,spatial.weights)
```
Estimate the number of subclusters, try 5, 10, or 20 pca components = nCOMP
```{r}
gc()
library(factoextra)
pca <- prcomp(t(log(networksubset[GeneMarkov,]+1)),scale. = FALSE)
cd_diffusionplot <-pca$x[,c(1:30)]
cd_diffusionplot <- cd_diffusionplot[!duplicated(cd_diffusionplot),]
ts <- Transitions(cd_diffusionplot,k=20)
pca <- prcomp(as.matrix(ts@transitions),scale. = FALSE)
plot(pca$sdev[1:100],pch = 20,
xlab = 'Diffusion component (DC)', ylab = 'sdev')
```
```{r}
nCOMP<- 5
pcaexpression <-  t(pca$x[,c(1:nCOMP)])
fviz_nbclust(t(pcaexpression),diss=dist(t(pcaexpression),method="manhattan"), hcut, method = "silhouette",
             hc_method = "ward.D2",k.max = 20)
```
```{r}
#View(as.matrix(ts@transitions))
#Networkdist <- 1*(as.matrix(ts@transitions) > 0)
Networkdist <- as.matrix(ts@transitions)
colnames(Networkdist) <- colnames(networksubset)
row.names(Networkdist) <- colnames(networksubset)
library(igraph)
L2graph <- graph_from_adjacency_matrix(Networkdist,weighted = TRUE,mode="undirected")
#L2graphSupercells <- cluster_walktrap(L2graph,weights=E(L2graph)$weight,step=50,merges=TRUE)
#table(L2graphSupercells$membership)

L2graphSupercells <- cluster_fast_greedy(L2graph,weights=E(L2graph)$weight)
table(L2graphSupercells$membership)
SCN3Eclustersubset <- as.factor(L2graphSupercells$membership)
names(SCN3Eclustersubset) <- L2graphSupercells$names
Networkdist <- as.dist(1-Networkdist)
fviz_nbclust(t(pcaexpression),diss=Networkdist, hcut, method = "silhouette",
             hc_method = "ward.D2",k.max = 20)
```
```{r, fig.height=5}
SCN3Egeneset <- GeneMarkov 
clusterdata <- log(networksubset[SCN3Egeneset,]+1)
clusterdata <- clusterdata[apply(clusterdata,1,function(x) var(x) > 0),apply(clusterdata,2,function(x) var(x) > 0)]
#library(cluster)
SCN3E_hcsubset <- hclust(dist(pca$x[,c(1:nCOMP)],method="manhattan"), method = "ward.D2")
#SCN3E_hcsubset <- hclust(Networkdist, method = "ward.D2")
SCN3Eclustersubset <- as.character(rbind(groups = cutree(SCN3E_hcsubset, k=10)))
names(SCN3Eclustersubset) <- colnames(clusterdata)
k=length(unique(SCN3Eclustersubset))
table(SCN3Eclustersubset)

pcagene <- prcomp(log(networkExpressionFile[row.names(clusterdata),]+1),scale. = FALSE)
pcageneexpression <- pcagene$x[,c(1:10)]
SCN3E_hc_gene <- hclust(dist(pcageneexpression,method="manhattan"), method = "ward.D2")



clusterz <-  networksubset[featureselection,]
Expression <- log(networksubset[featureselection,]+1)
diffclusters <- as.factor(SCN3Eclustersubset)
names(diffclusters) <- colnames(networksubset)
i=1
for(i in 1:length(levels(diffclusters)))
  {
  x <- Expression[,as.character(diffclusters) %in% levels(droplevels(diffclusters))[i]]
  x <- rowMeans(x)
  clusterz <- cbind(x,clusterz)
}
 clusterz <- clusterz[,ncol(clusterz)-ncol(Expression):ncol(clusterz)]
 colnames(clusterz) <- levels(droplevels(diffclusters))
 
 threshold <- mean(networksubset)
 Expression <- networksubset[featureselection,]
 clusterexp <-  networksubset[featureselection,]
 for(i in 1:length(levels(diffclusters)))
  {
  x <- Expression[,as.character(diffclusters) %in% levels(droplevels(diffclusters))[i]]
  x <- apply(x,1,function(x) length(x[x>=threshold])/length(x))
  clusterexp <- cbind(x,clusterexp)
}
 clusterexp <- clusterexp[,ncol(clusterexp)-ncol(Expression):ncol(clusterexp)]
 colnames(clusterexp) <- levels(droplevels(diffclusters))
 clusterexp <- row.names(clusterexp[apply(clusterexp,1,function(x) any(x>0.2)),])
 
 
clusterz <- scale(clusterz)
clusterz <- scale(t(clusterz))
clusterz <- t(clusterz)

clusterz <- clusterz[clusterexp,]
 

clusterfiltered <- clusterz[intersect(row.names(clusterz),SCN3Egeneset),]
nrow(clusterfiltered)

#tsne <- t(pca$x[,c(1:nCOMP)])


Networkdist <- as.matrix(ts@transitions)
Networkdist <- as.dist(1-Networkdist)
tsne <- Networkdist
library(Rtsne)
set.seed(123456789)
tsne_out <- Rtsne(t(tsne), initial_dims=20, perplexity=7+(0.01*ncol(networksubset)),max_iter = 1000,check_duplicates = FALSE,
                  verbose = TRUE, theta = 0.5, pca = FALSE)
#rownames(tsne_out$Y) <- colnames(tsne)



library("dendsort")

SCN3E_hcsubset <- dendsort(SCN3E_hcsubset, type="min")
SCN3E_hc_gene <- dendsort(SCN3E_hc_gene, type="min")
palette <- rainbow(length(levels(as.factor(SCN3Eclustersubset))))
cols <- palette[as.factor(SCN3Eclustersubset)]
library(heatmap3)
library(viridis)
heatmap3(clusterdata,ColSideColors=cols, Rowv = as.dendrogram(SCN3E_hc_gene) , Colv = as.dendrogram(SCN3E_hcsubset) ,scale = "col",symm = F, method = "ward.D2",col=viridis(256),balanceColor =F,cexRow = 0.8)
legend("topright", legend=levels(as.factor(SCN3Eclustersubset)),
   col=palette,
   pch=19)
plot(tsne_out$Y,col=cols,pch=20,cex=3)
legend("topright", legend=levels(as.factor(SCN3Eclustersubset)),
   col=palette,
   pch=19)
```
Check the expression of genes in clusterfiltered
```{r}
Expression2 <- as.data.frame(t(log(networksubset+1)))
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=Expression2$Cotl1)) +
  geom_point(size=1) + geom_density2d(alpha=0.0,size=0.5, color="black", bins=10)  + scale_colour_gradient(low = "grey", high = "red") +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")
```
Save clusterinfo and add the markers and clusters to a string and repeat the whole thing for other subclusters by increasing i to the corresponding cluster
```{r}
saveRDS(clusterfiltered, file =paste("~/Documents/SingleCellData/IdoDAM/",L1names[clusternumber],"markers.rds",sep=""))
write.table(clusterfiltered,file = paste("~/Documents/SingleCellData/IdoDAM/",L1names[clusternumber],"markers.txt",sep=""), sep="\t",row.names = TRUE, col.names = TRUE, quote = FALSE)

#If no clusters use
SCN3E_hcsubset <- hclust(Networkdist, method = "ward.D2")
SCN3Eclustersubset <- as.character(rbind(groups = cutree(SCN3E_hcsubset, k=1 )))
names(SCN3Eclustersubset) <- colnames(clusterdata)


#Add in the clusterinfo 
NetworkClusters <- c(NetworkClusters,paste(L1names[clusternumber],SCN3Eclustersubset,sep="_"))
namesNetworkClusters <- c(namesNetworkClusters,names(SCN3Eclustersubset))
L2markerlist <- c(L2markerlist,SCN3Egeneset)


```
Generate a tSNE using the found markers and specific genes in the clustering
```{r, fig.height=5}
L1L2markers <- c(L1geneset,L2markerlist)
#L1L2markers <- c(L1Markerslist,L2markerlist)
#L1L2markers <- L2markerlist
L1L2markers <- unique(L1L2markers)
names(NetworkClusters) <- namesNetworkClusters

pca <- prcomp(t(log(networkExpressionFile[L1L2markers,]+1)),scale. = FALSE)
tsne <-t(pca$x[,c(1:20)])

library(Rtsne)
set.seed(123456789)
tsne_out <- Rtsne(t(tsne), initial_dims=20, perplexity=7+(0.01*ncol(networkExpressionFile)),max_iter = 5000,check_duplicates = FALSE,
                  verbose = TRUE, theta = 0.5, pca = FALSE)
rownames(tsne_out$Y) <- names(NetworkClusters)
length(levels(as.factor(NetworkClusters)))

saveRDS(NetworkClusters[colnames(networkExpressionFile)], file = "~/Documents/SingleCellData/Networkclustering/SS2/SS2/Clusters/ClustersFinal.rds")

saveRDS(GeneMarkov, file = "~/Documents/SingleCellData/Networkclustering/SS2/SS2/Clusters/GeneMarkovOLstrict.rds")

diff <- readRDS("~/Documents/SingleCellData/ELISA10xanalysis/DifferentialExpression/Week1/Clustering/1markers.rds")

networkAnnotableFile$FinalClusters <- NetworkClusters[colnames(networkExpressionFile)]

#palette <- c("#b78ddd","#5bb84d","#9d55c7","#b5b233","#606ad9","#dd9230","#6891d8","#da582e","#46aed7","#dd3f5e","#54be9d","#cb4fb1","#3c8149","#d44385","#97b15e","#625ea3","#c99f5a","#984a79","#71732b","#d987c0","#9d5f2c","#e58095","#b63b33","#e58a6e","#aa4f57")
pdf("~/Documents/SingleCellData/IdoDAM/FinalTsne.pdf ",width = 10,height = 10,useDingbats=FALSE)
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=droplevels(as.factor(NetworkClusters[colnames(networkExpressionFile)])))) +
  geom_point(size=2) + geom_density2d(alpha=0.0,size=0.1, color="black", bins=10)  + (scale_colour_manual(as.factor(NetworkClusters[colnames(networkExpressionFile)]),values=palette))+
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")  +
 theme_bw() +
  theme(axis.line = element_line(colour = "black"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.border = element_blank(),
       panel.background = element_blank())


#Plot the tSNE
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=as.factor(NetworkClusters[colnames(networkExpressionFile)]))) +
  geom_point(size=2) + geom_density2d(alpha=0.0,size=0.1, color="black", bins=10)  + 
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")  +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.border = element_blank(),
       panel.background = element_blank())

#FinalClustersOrdered <- factor(networkAnnotableFile$FinalClusters, levels=c("OPC1a","OPC1b","OPC2","E17.5","COP","NFOL","Cycling","NP1a","NP1b","NP2","NP3","eVLMC","PLC","pnVLMC","VLMC"))
#palette <- c("#c6dbef","#6baed6","#08519c","#d03ea8","#006d2c","#41ab5d","#000000","#cab2d6","#6a3d9a","#dadaeb","#c994c7","#fcbba1","#ef3b2c","#a63603","#f16913")
#pdf("~/Documents/SingleCellData/Networkclustering/E13P7/L1clusteringtSNEAllgenes.pdf",width = 15,height = 10,useDingbats=FALSE)
ggplot(as.data.frame(tsne_out$Y), aes(x=V1, y=V2, colour=FinalClustersOrdered)) +
  geom_point(size=2) + geom_density2d(alpha=0.0,size=0.1, color="black", bins=10)  + (scale_colour_manual(as.factor(FinalClustersOrdered),values=palette))+
  theme(strip.background = element_blank(), strip.text.x = element_blank(),axis.text.x = element_blank(),axis.text.y= element_blank(),axis.ticks= element_blank(),axis.line  = element_blank(),panel.border = element_blank(),legend.position  = "right") + 
  xlab("tSNE_1") + ylab("tSNE_2")  +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.border = element_blank(),
       panel.background = element_blank())
```